Carbonate chemistry at Ny-Ålesund

### 2021-05-25 awipev-CO2.Rmd
start work on deconvolution

+ seawater pCO2 measured in the FerryBox on water pumped from 11 m depth.
+ atmospheric CO2 measured at the Zeppelin station and downloaded on 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999 
+ wind spreed data collected by the AWI at 10 m height (sent to JPG by P. Fischer, Aug. 2020)

@@

## Deconvolution of pCO2 changes
```{r pCO2 changes due to changes in T, S, AT and CT, include=FALSE}
# We follow the method of Garcia-Ibanez described above.
# construct a dataframe with monthly means for the entire series (mXX) as well as real data (without prefix m)
deconv_dat <- tibble(date=as.POSIXct(mean0m$sampling_date), mAT=means_month0m$AT[mean0m$monthd]*1e-6, mCT=means_month0m$CT[mean0m$monthd]*1e-6, mS=means_month0m$Salinity[mean0m$monthd], mT=means_month0m$Temperature[mean0m$monthd], P=mean0m$mean_P, Pt=mean0m$mean_Pt, Sit=mean0m$mean_Sit, AT=mean0m$mean_ta*1e-6, CT=mean0m$mean_dic*1e-6, S=mean0m$mean_salinity, T=mean0m$mean_temperature)
)

>>>>

+ seawater pCO2 measured in the FerryBox on water pumped from 11 m depth.
+ atmospheric CO2 measured at the Zeppelin station and downloaded on 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999 
+ wind speed data collected by the AWI at 10 m height (sent to JPG by P. Fischer, Aug. 2020)

@@

## Deconvolution of pCO2 changes
```{r pCO2 changes due to changes in T, S, AT and CT, include=FALSE}
# First we prepare data. CT is needed for deconvolution
# we calculate it from at_calc and pCO2
# nuts are not taken into consideration
deconv_dat <- d_all %>% # just for this chunk
  dplyr::select(datetime, sal_fb, temp_fb, pco2_fb, at_calc) %>% 
  dplyr::mutate(ct_calc = seacarb::carb(
    flag = 24, var1 = pco2_fb, var2 = at_calc, S=sal_fb, T=25, Patm=1, P=0, Pt=0, Sit=0,
        k1k2="x", kf="x", ks="d", pHscale="T", b="u74", gas="potential", 
        warn="y", eos="eos80", long=1.e20, lat=1.e20)

  ))

# We follow the method of Garcia-Ibanez described above.
# construct a dataframe with monthly means for the entire series (mXX) as well as real data (without prefix m)

deconv_dat <- tibble(date=as.POSIXct(mean0m$sampling_date), mAT=means_month0m$AT[mean0m$monthd]*1e-6, mCT=means_month0m$CT[mean0m$monthd]*1e-6, mS=means_month0m$Salinity[mean0m$monthd], mT=means_month0m$Temperature[mean0m$monthd], P=mean0m$mean_P, Pt=mean0m$mean_Pt, Sit=mean0m$mean_Sit, AT=mean0m$mean_ta*1e-6, CT=mean0m$mean_dic*1e-6, S=mean0m$mean_salinity, T=mean0m$mean_temperature)
)
